\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-23 papers/jss/article.Rnw
Note at the end of section 2 that the reflection based API is slightly slower for some operations, but that its much more convenient for interactive data analysis.
I want to tone down the implication that protocol buffers are the
best/fastest thing out there, and I always thought the 'particularly
well-suited' was a tad vague here.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@835 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

For added speed and efficiency, the \proglang{C++}, \proglang{Java},
and \proglang{Python} bindings to
Protocol Buffers are used with a compiler that translates a Protocol
Buffer schema description file (ending in \texttt{.proto}) into
language-specific classes that can be used to create, read, write, and
manipulate Protocol Buffer messages.  The \proglang{R} interface, in contrast,
uses a reflection-based API that is particularly well-suited for
interactive data analysis.  
All messages in \proglang{R} have a single class
structure, but different accessor methods are created at runtime based
on the named fields of the specified message type, as described in the
next section.

@@

<<>>=
p[["name"]] <- "Murray Stokely"
p[[ 2 ]] <- 3
p[[ "email" ]]
@

>>>>

For added speed and efficiency, the \proglang{C++}, \proglang{Java},
and \proglang{Python} bindings to
Protocol Buffers are used with a compiler that translates a Protocol
Buffer schema description file (ending in \texttt{.proto}) into
language-specific classes that can be used to create, read, write, and
manipulate Protocol Buffer messages.  The \proglang{R} interface, in contrast,
uses a reflection-based API that makes some operations slightly
slower but which is much more convenient for interactive data analysis.
%particularly well-suited for
%interactive data analysis.  
All messages in \proglang{R} have a single class
structure, but different accessor methods are created at runtime based
on the named fields of the specified message type, as described in the
next section.

@@

<<>>=
p[["name"]] <- "Murray Stokely"
p[[ 2 ]] <- 3
p[["email"]]
@
